---
title: "Authoring Websites with Rmarkdown, Github"
author: "Ben Best (bdbest@gmail.com)"
date: '`r format(Sys.time(), "%Y-%m-%d, Santa Barbara R Meetup")` '
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(vembedr)
```

## Example Websites

* [Environmental Data Scientist](http://benbestphd.com/)
* [Marine Biodiversity Observation Network](https://marinebon.github.io/)

## R Markdown

```{r}
embed_vimeo('178485416')
```

## R Markdown Websites

* [R Markdown Websites](http://rmarkdown.rstudio.com/rmarkdown_websites.html)

## Publishing to Github

Use **Github Pages** as free web hosting service. Can change domain to choice.

* [GitHub Pages - Websites for you and your projects, hosted directly from your GitHub repository. Just edit, push, and your changes are live.](https://pages.github.com/)
* [Bookdown: Authoring Books with R Markdown](https://bookdown.org/yihui/bookdown/github.html)

## Continuous Integration

Simply edit markdown (even with web browser on Github), and site will rebuild (within 10 min).

* [Bookdown: Authoring Books with R Markdown](https://bookdown.org/yihui/bookdown/github.html)
